A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface

### 2021-10-03 sections/methodology/main.tex
Add Nash Equilibrium subsection

\subsection{Nash Equilibrium}

>>>>

\subsection{Nash Equilibrium}\label{sec:methodology_nash_equilibrium}

Having calculated the payoff matrices \(A\) and \(B\), several algorithms can 
be used to help us find the Nash equilibrium of the game. 
The Nash equilibrium is the point of the game were both players have no 
incentive to deviate from their played strategies \cite{kreps1989nash}.
In other words their chosen strategies are a best response to each other.

The Lemke-Howson algorithm is used to get all Nash equilibria of the game 
\cite{LemkeHowson}.
Lemke-Howson uses best response polytopes to get one of the Nash equilibrium of
the game. 
By iterating over all possible dropped labels of the best response polytope all
Nash equilibria can be acquired.
All game theoretic calculations were done in Python using the Nashpy library 
\cite{axelrodproject}.
